### 2022-03-27 manuscript.tex
methods [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/78ef3a4ef4a18353bcca1019ff69fe0e3876a2bc.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/78ef3a4ef4a18353bcca1019ff69fe0e3876a2bc/checks
https://github.com/scherzerthesis/thesis/actions/runs/2048617253

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/aae47d7eb70a422d565a223f2ab9fc95ccae4700/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/aae47d7eb70a422d565a223f2ab9fc95ccae4700}{scherzerthesis/thesis@aae47d7}
on March 27, 2022.

@@

Adenoviral vectors and lentiviral vectors introduced in the lungs of GEMMs offer temporal control and can be titrated to acheive an optimal level of tumor numerosity. However, only lentiviral vectors can be used to barcode tumors because they integrate into the genome while adenoviruses do not(DuPage \emph{et al.}, 2009; Rogers \emph{et al.}, 2017). Together with CRISPR/CAS9 gene editing, lentiviruses have been used to analyzed many genetic interactions of oncogenic \emph{Kras} driven lung adenocarcinoma(Winters \emph{et al.}, 2017; Rogers \emph{et al.}, 2017). To enable simultaneous actvation of BRAF\textsuperscript{V600E} and loss of tumor supressor genes, we bred \emph{Braf\textsuperscript{CAT}}; \emph{H11b\textsuperscript{LSL-CAS9/+}} mice.
To determine the size of BRAF \textsuperscript{V600E} tumors and the contribution of 11 tumor suppressor genes (\emph{Trp53, Rb1, Cdkn2a, Apc, Rbm10, Stk11, Setd2, Arid1a, Atm, Keap1, Smad4)} on BRAF \textsuperscript{V600E} lung tumorigenesis, we obtained tittered barcoded-lentiviral plasmids that encode Cre-recombinase as well as a sgRNA that inactivates one of eleven tumor suppressors common in lung adenocarcinoma. All genes tested are putative tumor suppressor genes commonly lost in human lung cancer patients. Each lentiviral solution contained \textasciitilde1000 individually barcoded lentiviruses. We infected both \emph{LSL-Cas9} and \emph{CAS9} deficient mice in order to determine the contribution of genetic manipulation and/or deletion of the targeted gene. Mice meant to be analyzed after 8 weeks received a viral titer of 1x10\^{}5 while mice mean to be analyzed after 16 weeks received a viral titer of 1x10\^{}4. After euthanasia, lungs were collected for genomic DNA extraction, and barcode amplification followed by preperation of sequencing libraries. Before genomic extraction and library preparation, a known quantity of known-barcoded cells was added in order to benchmark sequencing reads to a known cell number.

@@

\textbf{test}

@@

@@

@@

@@

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/78ef3a4ef4a18353bcca1019ff69fe0e3876a2bc/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/78ef3a4ef4a18353bcca1019ff69fe0e3876a2bc}{scherzerthesis/thesis@78ef3a4}
on March 27, 2022.

@@

Adenoviral vectors and lentiviral vectors introduced in the lungs of GEMMs offer temporal control and can be titrated to acheive an optimal level of tumor numerosity. However, only lentiviral vectors can be used to barcode tumors because they integrate into the genome while adenoviruses do not(DuPage \emph{et al.}, 2009; Rogers \emph{et al.}, 2017). Together with CRISPR/CAS9 gene editing, lentiviruses have been used to analyzed many genetic interactions of oncogenic \emph{Kras} driven lung adenocarcinoma(Winters \emph{et al.}, 2017; Rogers \emph{et al.}, 2017). To enable simultaneous actvation of BRAF\textsuperscript{V600E} and loss of tumor supressor genes, we bred \emph{Braf\textsuperscript{CAT}}; \emph{H11b\textsuperscript{LSL-CAS9/+}} mice.
To determine the size of BRAF \textsuperscript{V600E} tumors and the contribution of 11 tumor suppressor genes (\emph{Trp53, Rb1, Cdkn2a, Apc, Rbm10, Stk11, Setd2, Arid1a, Atm, Keap1, Smad4)} on BRAF \textsuperscript{V600E} lung tumorigenesis, we obtained tittered barcoded-lentiviral plasmids that encode Cre-recombinase as well as a sgRNA that inactivates one of eleven tumor suppressors common in lung adenocarcinoma. All genes tested are putative tumor suppressor genes commonly lost in human lung cancer patients. Each lentiviral solution contained \textasciitilde1000 individually barcoded lentiviruses. We infected both \emph{LSL-Cas9} and \emph{CAS9} deficient mice in order to determine the contribution of genetic manipulation and/or deletion of the targeted gene. Mice meant to be analyzed after 8 weeks received a viral titer of 1x10\^{}5 while mice mean to be analyzed after 16 weeks received a viral titer of 1x10\^{}4. After euthanasia, lungs were collected for genomic DNA extraction, and barcode amplification followed by preperation of sequencing libraries. Before genomic extraction and library preparation, a known quantity of known-barcoded cells was added in order to benchmark sequencing reads to a known cell number(figure).

We determined the mean size of a BRAF\textsuperscript{V600E} driven tumor to be 21,248 thousand cells (figure). Interestingly, there is a widespread distribution of tumor sizes with the largest BRAF\textsuperscript{V600E} tumor to be \textasciitilde300,000 cells along with many small tumors (figure).

@@

\textbf{Animal husbandry}All mice were housed in an environmentally controlled room, and all animal care and experimental procedures were approved by (and in accordance with) the Institutional Animal Care and Use Committee Office of the Huntsman Cancer Institute at the University of Utah. Genetically engineered mouse breeding and genotyping was conducted as previously described (van Veen \emph{et al.}, 2019). The BRAF\textsuperscript{CAT} and \emph{Trp53\textsuperscript{fl/fl}} mice were previously described (Jonkers \emph{et al.}, 2001; van Veen \emph{et al.}, 2019; Dankort \emph{et al.}, 2007; Shai \emph{et al.}, 2015). All viruses were administered in a Biosafety Level 2+ room, as is regulated by the Institutional Biosafety Committee Guidelines. Adeno-SPC-CRE virus (University of Iowa) was delivered through nasal instillation. The \emph{Trp53\textsuperscript{wmR172H}} and \emph{Trp53\textsuperscript{wmR245W}} mice and respective genotyping protocols were gifted by Gigi Lozano and her laboratory and previously published (Zhang \emph{et al.}, 2018; Kim \emph{et al.}, 2021).

\textbf{Cell line generation}Tumor bearing mice were euthanized and lungs dissected. Lungs were then minced and incubated in digestive enzymes Collagenase I, dispase, elastase, for 30 minutes at 37 degrees. Single-cell suspensions were then resuspended in complete DMEM medium and filtered through a 100 micron filter and centrifuged at 300 x g for 5 minutes. Single-cell suspensions were then incubated in red blood cell lysis buffer for 5 minutes at room temperature, then resuspended in complete RPMI and placed in a tissue culture incubator. Cells were then passaged once a week with differential trypsinization to purify tumors cells from viable stromal cells. p53 status and BRAF\textsuperscript{V600E} status (tdTomato+) were assessed by western blot and flow cytometry.

\textbf{Tissue culture}Murine tumor derived cell lines and HCC-3564 cells were routinely cultured in DMEM supplemented with 10\% heat-inactivated FBS and 1\% penicillin/streptomycin. Cells were routinely tested for mycoplasma.

\textbf{Immunoblotting}Cells destined for western blot were scraped in ice cold PBS then centrifuged to pellet cells. After supernatant aspiration, cells were lysed with RIPA buffer supplemented with a protease/phosphatase inhibitor cocktail (Halt). Cell lysate protein concentration was determined with BCA assay. 40 microgram/lane was mixed with 4X SDS buffer and 10X sample buffer. Samples were run through a 4-12\% Bis-tris gel at 200V for approximately 75 minutes then transferred to a PVDF membrane using the iBlot2 transfer apparatus. Membranes were then incubated in Odyssey blocking buffer for 30 minutes before being incubated overnight with primary antibody. Membranes were then washed 3X with TBS-T and incubated in secondary antibody for 2 hours before being washed 3X and imaged on the Licor Odyssey clX.

\textbf{RNA Sequencing}Cells lines were routinely cultured for approximately 10 passages before RNA purification using Qiagen Mini kit from one million cells. Libraries were generated with Illumina TruSeq Stranded mRNA Library Prep with UDI kit and sequenced on a Nova-Seq targeting 25 million reads per sample. fastq files were processed on Galazy.org using FastQC, HISAT2, MultiQC, FeatureCounts, and DESeq2.

\textbf{Immunohistochemistry and immunofluoresence}Immunohistochemistry was performed as previously described, with the rabbit primary antibody against P53, SPC, phospho-ERK1/2, NKX2-1, HMGA2, p19/ARF (Mollaoglu \emph{et al.}, 2017; van Veen \emph{et al.}, 2019).

\textbf{Slide imaging and Quantification}Hematoxylin and eosin (H\&E) and IHC stained slides 1 were scanned automatically by the 3D Histech Pannoramic MIDI scanner (Thermo Fisher). Slides were imaged and analyzed using Caseviewer Software or QuantCenter analytical center provided on the 3D Histech Slide Scanner at the indicated magnification. Tumor burden was manually calculated on each lung lobe and total tumor area was compared to total lung area. Tumor diameters were measured using QuantCenter software from 3D Histech.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1624}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1709}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2308}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1368}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2991}}@{}}
\caption{\textbf{Critical reagents} \label{tbl:reagents}}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Reagents List}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reagent Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Source
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Catalog number
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Reagents List}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reagent Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Source
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Catalog number
\end{minipage} \\
\midrule
\endhead
antibody & beta-Actin & CST & 3700T & wb: 1:10,000 \\
antibody & Phospho ERK1/2 & CST & 4370 & wb:1:2000, IHC:1:1000 \\
antibody & ERK1/2 & CST & 4696 & wb: 1:2000 \\
antibody & P53 & Leica & cm-5 & wb: 1:2000, IHC: 1:1000, IF:1:250 \\
antibody & NKX2-1 & Abcam & ab76013 & IHC: 1:1000 \\
antibody & Pro-SPC & Millipore & Cat\# AB3786 & IHC: 1:2000 \\
antibody & HMGA2 & CST & 8179S & IHC 1:2000 \\
antibody & p19/ARF & Chuck Sherr & (Bertwistle \emph{et al.}, 2004) & \\
Cell Line & 293T & ATCC & CRL-3216 & \\
Cell Line & HCC-364 & Bivona lab & (Lin \emph{et al.}, 2014) & \\
Recombinant DNA & Pmd2.5 & Addgene & \#12259 & \\
Recombinant DNA & pspax2 & Addgene & \#12260 & \\
Recombinant DNA & P53-R175H & Addgene & \#22936 & \\
Chemical Compound & dabrafenib & Selleck & S2807 & \\
Chemical Compound & PLX4720 & Plexxikon/ Research Diets & & \\
Chemical Compound & trametinib & Selleck & S2673 & \\
Other & Collagenase type 1 & Thermo Fischer Scientific & 17100017 & \\
Other & Dispase & Corning & 354235 & \\
other & Elastase & Worthington Biochem & LS006365 & \\
other & ad5spc-Cre & university of Iowa & VVC-Berns1168 & \\
\bottomrule
\end{longtable}

@@

\leavevmode\vadjust pre{\hypertarget{ref-18dmdoj17}{}}%
Bertwistle,D. \emph{et al.} (2004) \href{https://doi.org/10.1089/hyb.2004.23.293}{Monoclonal antibodies to the mouse p19(Arf) tumor suppressor protein.} \emph{Hybrid Hybridomics}, \textbf{23}, 293--300.

@@

\leavevmode\vadjust pre{\hypertarget{ref-kGt16xDw}{}}%
Jonkers,J. \emph{et al.} (2001) \href{https://doi.org/10.1038/ng747}{Synergistic tumor suppressor activity of BRCA2 and p53 in a conditional mouse model for breast cancer.} \emph{Nat Genet}, \textbf{29}, 418--25.

@@

\leavevmode\vadjust pre{\hypertarget{ref-WiSGMfl3}{}}%
Lin,L. \emph{et al.} (2014) \href{https://doi.org/10.1073/pnas.1320956111}{Mapping the molecular determinants of BRAF oncogene dependence in human lung cancer.} \emph{Proc Natl Acad Sci U S A}, \textbf{111}, E748--57.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Rky3nm5Q}{}}%
Mollaoglu,G. \emph{et al.} (2017) \href{https://doi.org/10.1016/j.ccell.2016.12.005}{MYC Drives Progression of Small Cell Lung Cancer to a Variant Neuroendocrine Subtype with Vulnerability to Aurora Kinase Inhibition.} \emph{Cancer Cell}, \textbf{31}, 270--285.
